Graph bipartitioning and you

### 2016-01-09 evolutionaryComputation/2-practical/report.tex
Implemented ILS and GLS

\section{TODO}
MLS with several results
\end{document}

>>>>

While implementing ILS, I had it turn out results much worse than MLS.
The initial implmentation would just stop if it found a worse local optimum.
The description sais it should go back to the previous optimum. So I guess
that you should try again after that? But then I wonder how often you should
try again.

I got much better results with a system where the local search got several chances.
If it failed it would fallback, and then try again. 
With chances around 30 I managed to get up and around 1900.
When I reset the chance counter on a succesfull find
I managed to get consistently 2200, one result was as high as 2310.

I don't think there is a way to do it any better without drastically making
the algorithm more complex.
This current search for improvement was just based on the fact that ILS was
underperforming to MLS, which shouldn't be the case according to my memory
from the classes. Now its overperforming quite drastically so I'm happy.

I implemented GLS with the evolution class. The only thing I had to do really
was write the crossover method, the rest was already functional.
\section{TODO}
MLS with several results
\end{document}
